An Automatic Verification Framework for Software Configurations

### 2016-05-08 OSDI/eval.tex
config: eval

We mainly conduct three parts of experiments to evaluate our \app
prototype.

We want to answer several questions:

@@

>>>>

We mainly conduct three parts of experiments to evaluate our \app
prototype. We want to answer several questions:

@@

\begin{table*}[t]
\centering
\caption{Sampled benchmarks for misconfiguration detection}
\label{table-casestudy}
\begin{tabular}{|l|l|l|l|}
\hline
{\bf ID} & {\bf Problem Description} & {\bf Error Type} & 
{\bf \app Report}  \\ 
\hline
\hline
1 & How to configure MySql master slave to  
& Type Error 
& Expected a Filepath with P=1.0 \\ & backup master to slave & 
& for log-bin[mysqld] \\ \hline

2 & data import from MySql dies when MySQL  
& Correlation 
& Expected thread\_cache\_size[mysqld] > \\ & query limit is removed 
& & innodb\_buffer\_pool\_size \\ \hline

\end{tabular}
\end{table*}
